SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-08 2017-Xudong-SMT/ActaInformatica.tex
page 21, + bibref + reviews,docx

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}. 
\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, which is $\{v\leftarrow 0\}$, for its open automata.}
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} 
\YX{that the two open automata are equivalent with respect to a notion of FH-bisimulation.}
%how to prove that they are bisimilar.

@@

Figure~\ref{schema:ArchFailure:BIP} shows a refined version of the
Failure Monitor architecture used in~\cite{CubETH-case-study}.
%
The architecture consists of 2 \emph{coordinator components}
($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
%
%% Contrary to standard BIP models, architectures comprise one or several
%% \emph{operand} components, whereof only the set of \emph{ports} is
%% given.  Here, the operand component is $\NameOprnd$ and its interface
%% consists of the ports $\PortResume$ and $\PortFail$.
%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
%% $\NameTimer$\mdash are standard
The  \emph{behaviour} of BIP components %% insofar as they also
%% have their 
is specified by finite automata extended with
local data variables.  Transitions of these automata are labelled with
the ports of the corresponding components, Boolean guards and update
functions on local variables.  %% For instance, the loop transition
%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
%% can be fired only when the current value of the local variable $t$ is
%% lower than $Max$.  Upon firing, this transition increments the value
%% of $t$ by $1$.  When omitted, the default guard (\resp update
%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
%% architecture.
Although this is not visible in the figure, below we will assume that
the dangling ports $\PortFail$ and $\PortResume$ belong to the operand
component, whereas the dangling ports $\PortTick$, $\PortAsk$ and
$\PortReset$ represent actions of the environment.

>>>>

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}. 
\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, which is $\{v\leftarrow 0\}$, for its open automata.}
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} 
\YX{that the two open automata are equivalent with respect to a notion of (symbolic) FH-bisimulation.}
%how to prove that they are bisimilar.

@@

\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components. We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}

Figure~\ref{schema:ArchFailure:BIP} shows this refined version of the
Failure Monitor architecture used in~\cite{CubETH-case-study}.
%
The architecture consists of 2 \emph{coordinator components}
($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
%
%% Contrary to standard BIP models, architectures comprise one or several
%% \emph{operand} components, whereof only the set of \emph{ports} is
%% given.  Here, the operand component is $\NameOprnd$ and its interface
%% consists of the ports $\PortResume$ and $\PortFail$.
%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
%% $\NameTimer$\mdash are standard
The  \emph{behaviour} of BIP components %% insofar as they also
%% have their 
is specified by finite automata extended with
local data variables.  Transitions of these automata are labelled with
the ports of the corresponding components, Boolean guards and update
functions on local variables.  %% For instance, the loop transition
%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
%% can be fired only when the current value of the local variable $t$ is
%% lower than $Max$.  Upon firing, this transition increments the value
%% of $t$ by $1$.  When omitted, the default guard (\resp update
%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
%% architecture.
Although this is not visible in the figure, below we will assume that
the dangling ports $\PortFail$ and $\PortResume$ belong to the operand
component, whereas the dangling ports $\PortTick$, $\PortAsk$ and
$\PortReset$ represent actions of the environment.
